Ornaments as indicators of social changes and cultural practices in northeastern Taiwan before and after European colonial period

### 2019-12-10 analysis/paper/paper.Rmd
plot dates with ggplot2

# save the dataframe
write.csv(kw_age_cali_df_tidy, here("analysis/data/raw_data/kwl_cal_dates.csv"))

@@

# we can combine all the calibrated dates into a single plot, like this
kw_ages_densities <- 
  with(kw_dates_with_error,
       BchronDensity(
         ages = rce,
         ageSds = se,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce))
       ))

#plot it
plot(kw_ages_densities,
     xlab= "Years BC")

>>>>

@@

# we can combine all the calibrated dates into a single plot, like this
kw_ages_densities <- 
  with(kw_dates_with_error,
       rrtools:::quietly( # suppress the progress bar
         BchronDensity(
         ages = rce,
         ageSds = se,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce))
       ,
       store_density=TRUE))
  )

#plot it
plot(kw_ages_densities)

kw_ages_densities_df <- 
  tibble(ageGrid = kw_ages_densities$ageGrid,
         densities = kw_ages_densities$densities)

kw_ages_densities_dfs <- 
  map_df(kw_ages_densities$calAges, 
      ~tibble(ageGrid = .x$ageGrid, 
              densities = .x$densities), .id = 'date') %>% 
  mutate(dens_to_one = densities / sum(densities))

lower_component <- c(1300, 800)
upper_component <- c(600, 100)

ggplot() +
    geom_vline(xintercept = c(324,   # start of Euro contact, 1626 AD
                            182),  # start of Chinese contact, 1768 AD
                            colour = "red") +
    geom_area(data = kw_ages_densities_dfs,
            aes(ageGrid,
                dens_to_one,
                group = date),
            fill = "grey80",
            alpha = 0.4,
            position = 'identity') +
  geom_line(data = kw_ages_densities_df,
            aes(ageGrid,
                densities)) +
  annotate("rect", xmin = 100, xmax = 600, # upper_component
                   ymin = 0, ymax = Inf,
           fill = "grey80",
           alpha = 0.3) +
    annotate("text", x = 350, y = 0.007,
           label = "Upper component") +
    annotate("rect", xmin = 1300, xmax = 800,
                   ymin = 0, ymax = Inf,
           fill = "grey80",
           alpha = 0.3) +
      annotate("text", x = 1050, y = 0.007,
           label = "Lower component")  +
  theme_minimal(base_size = 14) +
  xlab("calibrated years BP") +
  ylab("Density")
